%% start of file
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,roman]{moderncv} % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault} % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc} % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8} % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% set fonts
%\setmainfont{Palatino Linotype}
%\setsansfont{Helvetica}

% adjust the page margins
\usepackage[perpage,bottom,stable]{footmisc}
\usepackage[vmargin=2cm,hmargin=2.5cm]{geometry}
\setlength{\hintscolumnwidth}{2.5cm} % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm} % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Qingyu}{Sui}
%\address{\#401, Zhichundongli, Zhichun Road, Haidian District}{Beijing, China}{China} % optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+86~186~0057~4747} % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{sqybilly@gmail.com} % optional, remove / comment the line if not wanted
\social[linkedin]{sqybi} % optional, remove / comment the line if not wanted
\social[github]{sqybi} % optional, remove / comment the line if not wanted

%\title{Resumé title} % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
%\homepage{sqybi.com} % optional, remove / comment the line if not wanted
%\social[twitter]{sqybi} % optional, remove / comment the line if not wanted
%\extrainfo{additional information} % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture} % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote} % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-1cm}

\section{Education}
\cventry{2009 -- 2013}{B.S. of Computer Science and Engineering}{Shanghai Jiao Tong University (SJTU)}{}{}{}

\section{Experience}
\cventry{2017 -- Present}
        {Software Engineer}
        {}
        {TuSimple Beijing}
        {}
        {\begin{itemize}%
         \item Integration Team.
               \begin{itemize}%
               \item Lane Fitting Service\newline{}%
                     This service is a wrapper for our machine learning based lane fitting algorithm. It can get video input from Point Grey camera, get raw lane information by the lane fitting algorithm, then re-format and send it to Human Machine Interface (HMI) and CAN bus on the truck.\newline{}%
                     It also works as a bridge between CAN bus and HMI. HMI can send some commands to CAN bus by communicating with Lane Fitting Service, as well as get car status (speed, throttle, etc.) from it.\newline{}%
                     Responsible for design and implementation of the whole system.
               \item Hwcap Video Collection System on TX1\newline{}%
                     Hwcap is a multi-way input video collection system which works on NVIDIA Jetson TX1 embedded platform. It will collect eight-way videos from eight cameras which is connected to three MAX9286 Deserializers\footnotemark[1]{}, and then process, encode, compress and store the video using the hardware encoding module on TX1. It can also check its own working status and report to a central server.\newline{}%
                     Responsible for design of the whole system and implementation of the TX1 video collection/encoding/storage part.
               \end{itemize}
         \end{itemize}}
         \footnotetext[1]{MAX9286: \link{https://www.maximintegrated.com/en/products/interface/high-speed-signaling/MAX9286.html}}
\cventry{2015 -- 2016}
        {Software Engineer}
        {}
        {Google}
        {}
        {\begin{itemize}%
         \item Mesa Team, DIA.
               Mesa\footnotemark[2]{} is a storage system in Google Ads infrastructure.
               \begin{itemize}%
               \item Modern Schema\newline{}%
                     Modern Schema is the metadata which contains table definition, table structures, read/write ACLs, etc.\newline{}%
                     Responsible for some new features and migration work in Modern Schema, such as allowing inheritance for ACLs, organizing and migrating thousands of schema files and fixing their dependencies, etc.
               \item Columnar Encoder/Decoder Optimization\newline{}%
                     Columnar is a new data storage format for Mesa which can improve performance for queries which doesn't require result from all columns.\newline{}%
                     Responsible for optimizing existing encoders/decoders and compressor for Columnar, implementing new encoders/decoders, and run benchmark on all of them to analyze the performance.\newline{}%
                     Aim to improve performance and compression rate of the encoders, while not affecting the query speed a lot.
               \end{itemize}
         \end{itemize}}
         \footnotetext[2]{Mesa: Geo-replicated, near real-time, scalable data warehousing, \textit{Proceedings of the VLDB Endowment}}
\cventry{2013 -- 2015}
        {Software Development Engineer}
        {}
        {Microsoft}
        {}
        {\begin{itemize}%
         \item Ads SCP Team, ASG.
               Responsible for fixing some bugs and implementing useful tools for team.
         \item Spartan Team, ASG.
               \begin{itemize}%
               \item Execution Broker Engine for Metadata Platform\newline{}%
                     An engine which takes some requirements of moving data from one storage to another, then execute and monitor them on an internal job scheduling platform. This is for Office 365 Big Data Platform and some other internal customers.\newline{}%
                     Responsible for the design and implementation of whole engine together with other two colleagues.
               \end{itemize}
         \item (Cortana) Proactive Experience Team, Information Platform and Experiences, STC.
               \begin{itemize}%
               \item Cortana Proactive Canvas Experience\newline{}%
                     Implemented a traslation suggestion feature for Cortana. It will suggest some useful expressions in local language base on user's current location, permanent residence, current local time, etc.\newline{}%
                     Responsible for design of the back-end, and implementation for both back-end and front-end.
               \item Diagnostic Dashboard for Cortana\newline{}%
                     A diagnostic infrastructure for Cortana developers with user-friendly frontend.\newline{}%
                     Responsible for some of the end-to-end debug scenarios, including log collection, log processing, user interface (HTML and Javascript/JQuery) and so on.
               \end{itemize}
         \item Activity Storage Team, MSN Social and Community Platform, STC.
               \begin{itemize}%
               \item Image Storage\newline{}%
                     The image storage backend for Bing Score.\newline{}%
                     Responsible for a performance test framework on Azure for this storage.
               \item Activity Storage\newline{}%
                     A no-SQL storage as the backend of MSN, Bing Score, etc., aimed for a real-time, high reliability and geo-replicated in-memory storage service.\newline{}%
                     Responsible for evaluation and improvement of performance.
               \end{itemize}
         \end{itemize}}

\section{Experience (Part-time and Intern)}
\cventry{2013}
        {Research Intern}
        {Visulization Group, Internet Graphics}
        {Microsoft Research Asia}
        {}
        {Visualization for large-scale evolving text streams based on rose tree.\footnotemark[3]{}}
        \footnotetext[3]{How Hierarchical Topics Evolve in Large Text Corpora, \textit{IEEE InfoVis 2014}}
\cventry{2012}
        {SDE Intern}
        {SQL Dev Group, STB}
        {Microsoft}
        {}
        {Responsible for implementing the NoInit feature in Sync Framework (Data Sync Service), to speed up the initial sync process.}
\cventry{2012}
        {Popular Science Writer}
        {}
        {Guokr\footnotemark[4]{}}
        {}
        {Write popular science articles\footnotemark[5]{} of Math and Informatics area for Guokr.com (in Chinese).}
        \footnotetext[4]{Guokr: \link{http://www.guokr.com/}}
        \footnotetext[5]{Articles on Guokr: \link{http://www.guokr.com/i/0492216944/articles/}}
\cventry{2011}
        {Developer}
        {Undergraduate Transcript and Certificate of Standing Transaction System}
        {SJTU Office of Academic Affairs}
        {}
        {Responsible for developing the online ordering logic and the interface between this system and Campus Payment system.}
\cventry{2010}
        {Teaching Assistant}
        {Data Structure}
        {SJTU}
        {}
        {Worked as the teaching assistant of the data structure course in SJTU.\newline{}%
         Responsible for grading, discussion and taking over class for absent instructor\footnotemark[6]{}, etc.}
        \footnotetext[6]{Instructor: Prof. Yu (\link{http://apex.sjtu.edu.cn/apex\_wiki/yyu})}
%\cventry{2009}{Team member}{ACM/ICPC}{Shanghai Jiao Tong University}{}{Joined SJTU ACM team in 2009.}
%\cventry{2008 -- 2009}{Teacher}{Xindi Education}{Tianjin}{}{Worked as teacher of Olympiad in Informatics (OI) in Xindi Education.}
\cventry{2009}
        {Developer}
        {PuTao\footnotemark[7]{}}
        {SJTU Network Center}
        {}
        {Responsible for the forum development.}
		\footnotetext[7]{PuTao: \link{http://pt.sjtu.edu.cn/}}
%\cventry{2009}{Tutor}{Shanghai Experimental High School}{Shanghai}{}{Worked as teacher of Olympiad in Informatics (OI) in Shanghai Experimental High School.}

\section{Publications}
\cventry{2014}
        {How Hierarchical Topics Evolve in Large Text Corpora\footnotemark[8]{}}
        {IEEE transactions on visualization and computer graphics}{}{}
        {Weiwei Cui, Shixia Liu, Zhuofeng Wu, Hao Wei}
        \footnotetext[8]{Worked on this paper during the internship at MSRA.}
\cventry{2014}
        {Clustering Image Search Results by Entity Disambiguation}
        {ECML/PKDD 2014}{}{}
        {Kaiqi Zhao, Zhiyuan Cai, Qingyu Sui, Enxun Wei and Kenny Zhu}
\cventry{2013}
        {CISC: Clustered Image Search by Conceptualization}
        {EDBT 2013}{}{}
        {Kaiqi Zhao, Enxun Wei, Qingyu Sui, Kenny Zhu and Eric Lo}

%\section{Projects}
%\cventry{2011 -- 2012}
%        {Context Extraction for Name Disambiguation on Structured Web Pages}{Participation in Research Program (PRP)}
%        {Advanced Data And Programming Technology Lab\footnotemark{}}
%        {SJTU}
%        {\begin{itemize}
%          \item{An algorithm which can extract context from a webpage with a specific entity name, used as a preprocessor for name disambiguation methods.}
%          \item{Developed majority of the algorithm, and finished the calibration of the test dataset, as a principal member of this project.}
%         \end{itemize}
%        }
%        \footnotetext{\link[http://www.cs.sjtu.edu.cn/$\sim$kzhu/adapt]{http://www.cs.sjtu.edu.cn/~kzhu/adapt}}
%\cventry{2012 -- present}
%        {Image Classification by Context Conceptualization}
%        {}
%        {Advanced Data And Programming Technology Lab}
%        {SJTU}
%        {\begin{itemize}
%          \item{Classify images in the search result of Google Image by textual information from their original webpages. We use incremental HAC as the clustering algorithm, Sibling and Wikification to extract signals from HTML text.}
%          \item{Responsible for the design and implementation of the core algorithm.}
%         \end{itemize}
%        }
%\cventry{2010 -- 2012}
%        {The Research and Development of Special Acoustic Directional Locator}
%        {The 2nd Shanghai Jiao Tong University Students' Innovative Practice Projects}
%        {}
%        {}
%        {\begin{itemize}
%          \item{A system which can react to special sound and locate the sound source.}
%          \item{Developed the Labview code in the project.}
%         \end{itemize}
%        }

\section{Awards}
\cventry{2009}
        {Google Codejam}
        {Top 500 Place}
        {}{}{}
\cventry{2008}
        {National Olympiad in Informatics (NOI)}
        {46th Place}
        {Silver Medal}
        {}{}
%\cventry{2009}{Youdao Nanti}{2nd Round}{}{}{}

\section{Skills}
\cvitem{Algorithm}
       {ACM/ICPC-level algorithmic problem-solving, Topcoder Algorithm Rating 1605\footnotemark9]{}.}
       \footnotetext[9]{TopCoder Profile: https://www.topcoder.com/members/sqybi/details/?track=DATA\_SCIENCE\&subTrack=SRM}
\cvitem{Language}
       {\textbf{C\#}, \textbf{C++}, \textbf{Python}.\newline{}%
        C, PHP, \LaTeX, HTML.}
        %Mathematica, SQL, Java, CSS
%\cvitem{Typography}
%       {Familar with typesetting in \LaTeX and graphics drawing in Asymptote.}
%\cvitem{General}
%       {Excellent ability of learning programming languages and algorithms, readily accepts new things.}
%        Friendly and easily getting along with other people.}
\end{document}

%% end of file.

